Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-10 paper/disc20clustering.tex
Avoiding repetitions
LB

A~\emph{ground set} is a group of nodes that repeatedly communicate when an algorithm splits them (places at different clusters).
Their role is to ensure that the algorithm maintains a~partition of ground sets into clusters.
We emphasize that ground sets are revealed only upon their nodes are split.
We say that a ground set is \emph{trivial} if it contains exactly one node.
We say that the node that belongs to trivial a ground set is \emph{isolated}.

The adversary constructs ground sets depending on the choices of a deterministic online algorithm.
We emphasize that the algorithm does not know ground sets before they are revealed.
Once we construct a ground set, it lasts until the end of the input sequence.

The constructed ground sets can be perfectly partitioned into the clusters (i.e., with nodes of each ground set collocated).
This way, the optimal algorithm moves to a perfect partition at the beginning (where requests incur the cost~$0$), thus its cost is bounded.
If the algorithm splits any pair of nodes of a ground set, the adversary issues requests to any pair of split nodes.
These two observations imply that the algorithm must eventually collocate all nodes of a~ground set to be competitive.

>>>>

A~\emph{ground set} is a group of nodes that repeatedly communicate when an algorithm splits them (places at different clusters).
Their role is to ensure that the algorithm maintains a~partition of ground sets into clusters.
We emphasize that ground sets are revealed only upon their nodes are split.
The adversary constructs ground sets depending on the choices of a deterministic online algorithm.
Once we construct a ground set, it lasts until the end of the input sequence.
We say that a ground set is \emph{trivial} if it contains exactly one node.
We say that the node that belongs to trivial a ground set is \emph{isolated}.

The ground sets constructed in this lower bound can be perfectly partitioned into the clusters (i.e., with nodes of each ground set collocated).
This way, the optimal algorithm moves to a perfect partition at the beginning (where requests incur the cost~$0$), thus its cost is bounded.
If the algorithm splits any pair of nodes of a ground set, the adversary issues requests to any pair of split nodes.
These two observations imply that the algorithm must eventually collocate all nodes of a~ground set to be competitive.
